%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Henry Crute} % Your name
\address{5117 N Lamar Blvd \\ Austin, TX 78751} % Your address
\address{10440 Rock Creek Dr \\ San Diego, CA 92131} % Your secondary addess (optional)
\address{(831)~$\cdot$~325~$\cdot$~8718 \\ henrycrute@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Texas at Austin} \hfill {\em August 2015 - May 2017} \\
M.S. in Electrical \& Computer Engineering \\
Academic Focus in Architecture, Computer Systems, and Embedded Systems \\

{\bf University of California, Santa Cruz} \hfill {\em September 2011 - June 2015} \\
B.S. in Computer Engineering \\
Minor in Computer Science \\
Member of Tau Beta Pi Engineering Honor Society \\
Dean's Undergraduate Research Award: May 2015 \\
Dean's Honors: Fall 2013 - Spring 2014 \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Qualcomm}{May 2016 - August 2016}{Modem Firmware Intern}{San Diego, CA}
\item Implemented a UE Specific Regerence Signal Interference Cancellation and Equalization algorithm.
\item Used a proprietary SIMD VLIW singnal processing architecture.
\item The final product accomplished matrix inverse approximations using an optimized combination of the Gauss-Seidel method, Cholesky decomposition, and backwards substitution over large non-sparse matrices of complex numbers.
\item Verified and validated the algorithms using Matlab, and C. Finally partially optimized in assembly.
\end{rSubsection}

\begin{rSubsection}{UC Santa Cruz}{June 2014 - June 2015}{Research Assistant}{Santa Cruz, CA}
\item Wrote PIC32 firmware for intermediate data flow control and processing between the MCP3912 sigma delta ADC and wifi/usb controllers.
\item Wrote firmware for the ESP8266-03 to store and http POST wattage data to a test server.
\item The ESP8266-03 firmware includes the use of an ad hoc chip configuration network as well as regular station mode to connect to the server end point.
\item Maintained MSP430 firmware for high speed voltage and current sampling.
\item Wrote data visualization software for big data with MATLAB and Python.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{CITRIS/ITI}{June 2014 - January 2015}{Technical Assistant}{Santa Cruz, CA}
\item Served in technical support for equipment in CITRIS conference rooms, experimental classrooms and videoconferencing facilities, for their audio-visual and teleconferencing equipment.
\item Helped manage conferences, research symposiums, classes, job fairs, and other events requesting CITRIS space.
\end{rSubsection}

\end{rSection}


\clearpage %%page break

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & C/C++, Embedded C, Python, Assembly, Java, \\
 & Matlab, Verilog, Perl \\
Communication \& Networking & TCP \& UDP IPs, PAM-N \& QAM-N Transceivers \\
Tools \& Platforms & Git, Mercurial, gem5, Code Composer, Eclipse, \\
 & MPLAB, NP++, Geany, FDATool, VCS
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Additional Example Projects}

\item {\bf x86 Processor} - Designed a processor with an x86 instruction set specified by the IA-32 Intel Architecture Software Developer's Manual in a team of four engineers. Built using only structural Verilog. The micro-architecture included a 7 stage pipeline, simple two level branch predictor, and i-cache, d-cache, DMA, I/O controllers sharing a 32 bit bus. The micro-architecture also handled interrupts, and precise exceptions.
\item {\bf SRRIP Replacement Policy} - Built using C++ and Python. Added the Static Re-Reference Interval Prediction policy in C++ to gem5 and compared it to the already implemented LRU policy. Statistics of cache misses for different associativity and sizes were obtained using python and SPEC CPU 2006 test benches.
\item {\bf Compiler} - Built using C++, Flex, and Bison. The compiler scans, parses, type checks, and outputs appropriately translated assembly code. The language is a subset of C, and includes structs, loops, variables, if statements, scope, functions, and more.
\item {\bf Foobar Challenges} - Built using python. Documented and solved numerous coding challenges in the topics of algorithms, data structures, low-level representation, math, and cryptography.

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
